---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

source("R/get_targeting.R")
```

# metatargetr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/metatargetr)](https://CRAN.R-project.org/package=metatargetr)
<!-- badges: end -->

The goal of metatargetr is to ...

## Installation

You can install the development version of metatargetr like so:

``` r
remotes::install_github("favstats/metatargetr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(metatargetr)
## basic example code
```

## Get Targeting criteria (Last 30 Days)

The following code retrieves the targeting criteria used by the Social Democrats in Denmark in the last 30 days. Just put in the right Page ID.

```{r cars}
last30<- get_targeting("41459763029", timeframe = "LAST_30_DAYS")

head(last30, 5)
```

## Get Targeting criteria (Last 7 Days)

The following code retrieves the targeting criteria used by the Social Democrats in Denmark in the last 7 days. Just put in the right Page ID.



```{r}
last7 <- get_targeting("41459763029", timeframe = "LAST_7_DAYS")


head(last7, 5)
```
